---
title: "CoxFlex package: Flexible modeling of the time-to-event data"
author: "Yishu Wang, Willy Wynant"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CoxFlex package: Flexible modeling of the time-to-event data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette documents the usage of the CoxFlex package, which implements a flexible extension of the Cox’s PH model allowing for non-linear (NL) and/or time-dependent (TD) effects of: 1) time-fixed; 2) time-varying covariates on the log hazard. The package also implements the backward elimination procedure to build flexible multivariable model for analyses that consider several, often inter-correlated, covariates with a priori unknown effects on the hazard. 

The usage of the functions in the CoxFlex package is illustrated through analyzing the data from the `survival` package as examples.  the use of the functions available in the FlexSurv package on an example with data available from the survival package. The current implementation of the FlexSurv package requires that the dataset is in an interval format. The FlexSurv package allows for fixed-in-time and time-dependent covariates. For additional statistical details on the selection and estimation of the flexible extension of the Cox’s model and its validation in simulations



## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
